---
title: "Clustering benchmark metric collection: clustering metrics"
author: "Izaskun Mallona"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    code_download: true
    number_sections: true
    df_print: kable
    theme: lumen
params:
  seed: 665
---

Caution this is a draft, not pretty!

This version globs results instead of getting them from a `metrics file` or arguments. Due to the active development of [PR 45](https://github.com/omnibenchmark/omnibenchmark/pull/45) and [PR 52](https://github.com/omnibenchmark/omnibenchmark/pull/52).


```{r}
library(argparse)
library(ggplot2)
library(tidyr)

```


```{r}
parser <- ArgumentParser(description="Clustering metric collector")


parser$add_argument('--input_dir',
                    type="character",
                    help='path to the `out` omnibenchmark results folder')

args <- parser$parse_args()

## args <- list(input_dir = '/home/imallona/src/clustering_example/out')
```

## Clustbench metrics

We'll have to read both metrics and param files? e.g. direct translation of [the python implementation](https://github.com/omnibenchmark/omnibenchmark/pull/45/files#diff-61e6034e7438befed44f7303987c35f814bdfee939eb70186b48dbe2fe1182c8)?



```{r}
## def tokenize(file_path: str):
##     ## we get only after the 'out' directory
##     fp = file_path.split("out/")[1].split("/")
##     ## and slice in stage/method/params triples
##     return [x for x in zip(*(iter(fp),) * 3)]

tokenize <- function(fn, out = 'out') {
    fn <- file.path(out, fn)
    fp = strsplit(strsplit(fn, split = 'out/')[[1]][2], split = '/')[[1]]
    i <- 1
    res <- list()
    while (i < length(fp)) {
        res[[as.character(i)]] <- fp[i:(i+2)]
        i <- i+3
    }
    return(res)
}

## def read_params(file_path: str):
##     triples = tokenize(file_path)
##     params_path = ""
##     res = ""
##     parent = "out"
##     for triple in triples:
##         parent = op.join(parent, triple[0], triple[1], triple[2])
##         if not "default" in triple[2]:
##             param_file_path = op.join(parent, "parameters.txt")
##             with open(param_file_path) as fh:
##                 reader = csv.reader(fh, delimiter="\t")
##                 for row in reader:
##                     res = "%s %s %s %s %s;" % (
##                         res,
##                         triple[0],
##                         triple[1],
##                         triple[2],
##                         row[0].strip(),
##                     )

read_params <- function(file_path, out = 'out') {
    triples <- tokenize(file_path)    
    params_path = ""
    res <- list()
    parent <- out
    for (i in 1:length(triples)){
        triple <- triples[[i]]
        parent = file.path(parent, triple[1], triple[2], triple[3])
        if (triple[3] != "default"){
            param_file_path <- file.path(parent, "parameters.txt")
            ## caution param files lack EOL
            params <- readLines(param_file_path, warn = FALSE)
            res[[i]] <- c(triple[1], triple[2], triple[3], params)
        }
    }
    return(res)
}
```


```{r read_metrics}

d <- list()

for (fn in list.files(args$input_dir, pattern = "clustbench.scores.gz", recursive = TRUE)){
    d[[fn]] <- list(
        run = read_params(out = args$input_dir, file_path = fn),    
        metrics = read.csv(file.path(args$input_dir, fn), header = TRUE))
}

str(d[1:3])
```

To plot the data we tabulate them first:

```{r}
## slot 1: data
## slot 2: next, typically method
## slot 3: typically metric
prettify_run <- function(x, slot) {
    ## 1 would be the stage, #2 the module name and ## 3 the param_x encoding, so discarding most
    return(gsub(',', '\n', x$run[[slot]][4]))
}


fd <- do.call(rbind.data.frame,
              lapply(d, function(x) {
                  run_fd <- data.frame(metric = prettify_run(x, 3),
                                       method = prettify_run(x, 2),
                                       data =   prettify_run(x, 1))
                  fd <- cbind(run_fd, unname(x$metrics))
                  return(fd)
              })
              )
fd$file <- rownames(fd)
rownames(fd) <- 1:nrow(fd)
colnames(fd) <- c('metric', 'method', 'data', 'k-2', 'k-1', 'k', 'k+1', 'k+2', 'file')
dim(fd)
```


```{r, fig.width = 20, fig.height = 15}
summary(fd)

pivot_longer(
    fd,
    cols = c('k-1', 'k-2', 'k', 'k+1', 'k+2'),
    names_to = 'ks') %>%
    ggplot(aes(x=ks, y= value, color = method)) +
    geom_point() +
    facet_grid(metric~data) +
    theme_bw()
```

## Resources

As calculated by the `benchmark` snakemake directives.


```{r}
sessionInfo()
```
